---
title: "MAC gene categories"
output: html_document
date: "2023-01-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(stringr)
library(tidyr)
library(viridis)
library(ggstatsplot) 
library(ggstatsplot) 
library(rstatix)
library(RVAideMemoire)
library(GOstats)
library(AnnotationForge)
library(GSEABase)
```

Create Metarhizium acridum datatable for orthogroups

```{r}
unassigned <- read.delim("Figure_2/d03_Orthogroups_UnassignedGenes.tsv")
orthogroups <- read.delim("Figure_2/d02_Orthogroups.tsv")

all_ortho <- rbind(orthogroups, unassigned)

mac <- all_ortho[c(1,2,18:23)]
mac[mac == ''] <- NA
mac_rm <- mac[rowSums(is.na(mac)) != 7, ]  

mac_rm$M.acridum_GCA_000187405.1 <- mac_rm$GCA_000187405.1
mac_rm$GCA_000187405.1 <- NULL

mac_binary <- mac_rm[ , 2:8]

mac_binary[mac_binary != "*"] = 1
mac_binary <- mac_binary %>% replace(is.na(.), 0)

mac_binary <- mutate_all(mac_binary, function(x) as.numeric(as.character(x)))
mac_binary$total <- rowSums(mac_binary)

p <- mac_binary %>% dplyr::count(total, sort = TRUE)
```


Make histogram of distribution 
```{r}
p$total <- as.factor(p$total)
p$n <- as.numeric(p$n)

cols <- c("#8b0000","#ff0000", "#ff0000", "#ff0000", "#ff0000", "#ff0000", "#ff9d9d")

bar_ortho <- ggplot(p) +
  geom_bar(stat = "identity", aes(x=total, y=n, fill=total)) +
  scale_fill_manual(values = cols) +
  theme_minimal()
bar_ortho
```


Determine number of singletons in each isolate
```{r}
singletons <- mac_binary %>% filter(total == 1) 

mac_singletons <- as.data.frame(colSums(singletons))
mac_singletons$isolate <- rownames(mac_singletons)
mac_singletons <- mac_singletons[-8,]
mac_singletons$count <- mac_singletons$`colSums(singletons)`

mac_singlebar <- ggplot(mac_singletons) +
  geom_bar(stat = "identity", fill="#8b0000", aes(x=isolate, y=count)) +
  theme_minimal()

mac_singlebar
```


Make tables for core, accessory, and singleton orthogroups 
```{r}
ortho_list <- mac_rm$Orthogroup
mac_binary$Orthogroup <- ortho_list

singletons <- mac_binary %>% filter(total == 1) 
core <- mac_binary %>% filter(total == 7) 
accessory <- mac_binary %>% filter(total < 7, total > 1)

single_ortho <- singletons$Orthogroup
core_ortho <- core$Orthogroup
acc_ortho <- accessory$Orthogroup

mac_rm$KVL_1801<-gsub("FUN","MAC1",as.character(mac_rm$KVL_1801))
mac_rm$KVL_1802<-gsub("FUN","MAC2",as.character(mac_rm$KVL_1802))
mac_rm$KVL_1803<-gsub("FUN","MAC3",as.character(mac_rm$KVL_1803))
mac_rm$KVL_1806<-gsub("FUN","MAC6",as.character(mac_rm$KVL_1806))
mac_rm$KVL_1807<-gsub("FUN","MAC7",as.character(mac_rm$KVL_1807))
mac_rm$KVL_1808<-gsub("FUN","MAC8",as.character(mac_rm$KVL_1808))

mac_rm$proteins <- apply(
  mac_rm[, c("KVL_1801","KVL_1802","KVL_1803",
             "KVL_1806","KVL_1807","KVL_1808",
             "M.acridum_GCA_000187405.1")],
  1,
  function(x) paste(na.omit(x), collapse = ",")
)

mac_proteins <- mac_rm %>%
  tidyr::separate_rows(proteins, sep = ",")

mac_long <- mac_proteins %>%
  dplyr::rename(id = proteins) %>%
  mutate(id = trimws(id)) %>%
  filter(id != "", !is.na(id))

single_df <- mac_long[mac_long$Orthogroup %in% single_ortho,]
acc_df <- mac_long[mac_long$Orthogroup %in% acc_ortho,]
core_df <- mac_long[mac_long$Orthogroup %in% core_ortho,]
```

Determine percentage of each genome that is accessory
```{r}
mac_acc <- mac_binary %>% filter(total < 7)

acc_proteins <- as.data.frame(colSums(mac_acc[, (1:7)]))

```

Determine length of genes in each compartment
```{r}
MAC_length <- read.delim("d02_MAC_length.txt", header=FALSE)
MAC_length$id <- MAC_length$V1 
MAC_length$V1 <- NULL

name1 <- "singleton"
name2 <- "accessory"
name3 <- "core"

single_df$category <- name1
acc_df$category <- name2
core_df$category <- name3

all_MAC <- rbind(single_df, acc_df, core_df)

MAC_merge <- merge(MAC_length,all_MAC,by="id", all.x = TRUE)

MAC_core <- MAC_merge %>% filter(category == "core")
MAC_acc <- MAC_merge %>% filter(category == "accessory")
MAC_sin <- MAC_merge %>% filter(category == "singleton")

ggplot(MAC_core, aes(x=V2)) +
  geom_histogram(bins=100)
ggplot(MAC_acc, aes(x=V2)) +
  geom_histogram(bins=100)
ggplot(MAC_sin, aes(x=V2)) +
  geom_histogram(bins=100)

summary(MAC_core$V2)
IQR(MAC_core$V2)
core_min <- 266.0-329
core_max <- 595+329
MAC_core_mod <- MAC_core %>% filter(V2 <= core_max)

summary(MAC_acc$V2)
IQR(MAC_acc$V2)
acc_min <- 149-313
acc_max <- 462+313
MAC_acc_mod <- MAC_acc %>% filter(V2 <= acc_max)

summary(MAC_sin$V2)
IQR(MAC_sin$V2)
sin_min <- 128-199.75
sin_max <- 327.8+199.75
MAC_sin_mod <- MAC_sin %>% filter(V2 <= sin_max)

MAC_IQR <- rbind(MAC_core_mod, MAC_acc_mod)
MAC_IQR <- rbind(MAC_IQR, MAC_sin_mod)

```

boxplot of gene sizes
```{r}
MAC_IQR$category <- as.factor(MAC_IQR$category)
MAC_IQR$category <- factor(MAC_IQR$category, levels = c("core", "accessory", "singleton"))

cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

gene_size <- MAC_IQR %>%
  ggplot(aes(x=category, y=V2, fill=category)) +
    geom_boxplot(width=0.8, alpha=0.7) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()

gene_size

```

Geom_flat_violin function
```{r}
#function 1
geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                        position = "dodge", trim = TRUE, scale = "area",
                        show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}

#function 2
GeomFlatViolin <-
  ggproto("GeomFlatViolin", Geom,
          setup_data = function(data, params) {
            data$width <- data$width %||%
              params$width %||% (resolution(data$x, FALSE) * 0.9)

            # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
            data %>%
              group_by(group) %>%
              mutate(ymin = min(y),
                     ymax = max(y),
                     xmin = x,
                     xmax = x + width / 2)

          },

          draw_group = function(data, panel_scales, coord) {
            # Find the points for the line to go all the way around
            data <- transform(data, xminv = x,
                              xmaxv = x + violinwidth * (xmax - x))

            # Make sure it's sorted properly to draw the outline
            newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                             plyr::arrange(transform(data, x = xmaxv), -y))

            # Close the polygon: set first and last point the same
            # Needed for coord_polar and such
            newdata <- rbind(newdata, newdata[1,])

            ggplot2:::ggname("geom_flat_violin", GeomPolygon$draw_panel(newdata, panel_scales, coord))
          },

          draw_key = draw_key_polygon,

          default_aes = aes(weight = 1, colour = "grey20", fill = "white", size = 0.5,
                            alpha = NA, linetype = "solid"),

          required_aes = c("x", "y")
)

#function 3
"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}
```


```{r}
test <-  ggplot(MAC_IQR, aes(x=category, y=V2, fill=category)) +
    geom_flat_violin(scale = "count", trim = FALSE, width=2) + 
    scale_fill_viridis(discrete = TRUE) +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "pointrange", color = "red") + 
    geom_dotplot(binaxis = "y", dotsize = 5, stackdir = "down", binwidth = 0.3, position = position_nudge(-0.025)) + 
    theme_ipsum() +
    theme(
      legend.position = "none"
    ) + 
    ylab("value")
 
test
```

Kruskal-Wallis test
```{r}
kruskal.test(V2 ~ category, data = MAC_IQR)

pairwise.wilcox.test(MAC_IQR$V2, MAC_IQR$category,
                 p.adjust.method = "BH")
```


Make bar charts for determining functions of genes in different genome compartments. We start with the secretome. These files can be found within the folder, d01_KVL_data_subsets
```{r}
#upload secretome files
KVL_1801_sec <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.secretome.txt", header=FALSE)
KVL_1802_sec <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.secretome.txt", header=FALSE)
KVL_1803_sec <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.secretome.txt", header=FALSE)
KVL_1806_sec <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.secretome.txt", header=FALSE)
KVL_1807_sec <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.secretome.txt", header=FALSE)
KVL_1808_sec <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.secretome.txt", header=FALSE)

#remove column 2
KVL_1801_sec$V2 <- NULL
KVL_1802_sec$V2 <- NULL
KVL_1803_sec$V2 <- NULL
KVL_1806_sec$V2 <- NULL
KVL_1807_sec$V2 <- NULL
KVL_1808_sec$V2 <- NULL

#remove reference genome from merged datatable
MAC_noref <- all_MAC[!grepl("FUN", all_MAC$id),]
MAC_noref <- MAC_noref %>%
  select(-KVL_1801, -KVL_1802, -KVL_1803,
         -KVL_1806, -KVL_1807, -KVL_1808,
         -`M.acridum_GCA_000187405.1`)

#change name of column for merging
names(KVL_1801_sec)[names(KVL_1801_sec) == "V1"] <- "id"
names(KVL_1801_sec)[names(KVL_1801_sec) == "V3"] <- "K1"
sec_MAC <- merge(MAC_noref,KVL_1801_sec, by="id", all.x = TRUE)

names(KVL_1802_sec)[names(KVL_1802_sec) == "V1"] <- "id"
names(KVL_1802_sec)[names(KVL_1802_sec) == "V3"] <- "K2"
sec_MAC <- merge(sec_MAC, KVL_1802_sec, by="id", all.x = TRUE)

names(KVL_1803_sec)[names(KVL_1803_sec) == "V1"] <- "id"
names(KVL_1803_sec)[names(KVL_1803_sec) == "V3"] <- "K3"
sec_MAC <- merge(sec_MAC, KVL_1803_sec, by="id", all.x = TRUE)

names(KVL_1806_sec)[names(KVL_1806_sec) == "V1"] <- "id"
names(KVL_1806_sec)[names(KVL_1806_sec) == "V3"] <- "K6"
sec_MAC <- merge(sec_MAC, KVL_1806_sec, by="id", all.x = TRUE)

names(KVL_1807_sec)[names(KVL_1807_sec) == "V1"] <- "id"
names(KVL_1807_sec)[names(KVL_1807_sec) == "V3"] <- "K7"
sec_MAC <- merge(sec_MAC, KVL_1807_sec, by="id", all.x = TRUE)

names(KVL_1808_sec)[names(KVL_1808_sec) == "V1"] <- "id"
names(KVL_1808_sec)[names(KVL_1808_sec) == "V3"] <- "K8"
sec_MAC <- merge(sec_MAC, KVL_1808_sec, by="id", all.x = TRUE)

sec_merge <- sec_MAC
sec_merge$sec <- paste(sec_merge$K1, "", sec_merge$K2, "", sec_merge$K3, "", sec_merge$K6, "", sec_merge$K7, "", sec_merge$K8)
sec_merge <- sec_merge %>%
  select(-matches("^K[123678]$"))
sec_merge$sec<-gsub("NA","",as.character(sec_merge$sec))
sec_merge$sec<-gsub(" ","",as.character(sec_merge$sec))

sec_merge$sec<-gsub("SEC.*","SEC",as.character(sec_merge$sec))
sec_merge["sec"][sec_merge["sec"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
sec_merge$id <- NULL

sec_unique <- sec_merge %>%
  count(Orthogroup, category, sec, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = sec[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
sec_summary <- sec_unique %>% group_by(category, first) %>% tally()

sec_total <- sec_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
sec_total$first <- total

sec_all <- rbind(sec_summary, sec_total)

sec_pivot <- sec_all %>% pivot_wider(names_from = first, values_from = n)
sec_pivot$percent <- (sec_pivot$SEC/sec_pivot$total) * 100

sec_pivot$category <- factor(sec_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_sec <- ggbarstats(data = sec_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_sec
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

sec_plot <- ggplot(sec_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
sec_plot

#chi square test
sec_test <- chisq.test(table(sec_unique$category, sec_unique$first))
sec_test
pairwise_prop_test(table(sec_unique$category, sec_unique$first), p.adjust.method = "BH")

```


Try with a different secretome method, as employed by funfinder. Not sure if this method is better, but it is more "strict" since it uses input from phobius and tmhmm to determine if some of the predicted secretome proteins are actually transmembrane (based on predictions of the number of transmembrane helices in each protein). The results are different, but until I have a better understanding of these programs, I think I will stick with the funannotate version. 
```{r}
#KVL_1801
pho_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/KVL_1801_phobius.results.txt", header=FALSE)
pho_1801_t <- pho_1801 %>% filter(V3 == "Y")
pho_1801_s <- pho_1801 %>% filter(V2 > 0)
pho_1801_t[ , 2:4] <- NULL
pho_1801_s[ , 2:4] <- NULL

tmhmm_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/KVL_1801_tmhmm.results", header=FALSE)
tmhmm_1801 <- separate(data = tmhmm_1801, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1801 <- tmhmm_1801 %>% filter(value > 0)
tmhmm_1801[ , 2:7] <- NULL

KVL_1801_sec <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.secretome.txt", header=FALSE)
KVL_1801_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1801 <- rbind(KVL_1801_sec, pho_1801_s)
sec_1801 <- distinct(sec_1801, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1801 <- as.data.frame(sec_1801[!(sec_1801$V1 %in% tmhmm_1801$V1),])
names(sec_1801)[names(sec_1801) == "sec_1801[!(sec_1801$V1 %in% tmhmm_1801$V1), ]"] <- "V1"
sec_1801 <- as.data.frame(sec_1801[!(sec_1801$V1 %in% pho_1801_t$V1),])
names(sec_1801)[names(sec_1801) == "sec_1801[!(sec_1801$V1 %in% pho_1801_t$V1), ]"] <- "V1"

#KVL_1802
pho_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/KVL_1802_phobius.results.txt", header=FALSE)
pho_1802_t <- pho_1802 %>% filter(V3 == "Y")
pho_1802_s <- pho_1802 %>% filter(V2 > 0)
pho_1802_t[ , 2:4] <- NULL
pho_1802_s[ , 2:4] <- NULL

tmhmm_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/KVL_1802_tmhmm.results", header=FALSE)
tmhmm_1802 <- separate(data = tmhmm_1802, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1802 <- tmhmm_1802 %>% filter(value > 0)
tmhmm_1802[ , 2:7] <- NULL

KVL_1802_sec <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.secretome.txt", header=FALSE)
KVL_1802_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1802 <- rbind(KVL_1802_sec, pho_1802_s)
sec_1802 <- distinct(sec_1802, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1802 <- as.data.frame(sec_1802[!(sec_1802$V1 %in% tmhmm_1802$V1),])
names(sec_1802)[names(sec_1802) == "sec_1802[!(sec_1802$V1 %in% tmhmm_1802$V1), ]"] <- "V1"
sec_1802 <- as.data.frame(sec_1802[!(sec_1802$V1 %in% pho_1802_t$V1),])
names(sec_1802)[names(sec_1802) == "sec_1802[!(sec_1802$V1 %in% pho_1802_t$V1), ]"] <- "V1"

#KVL_1803
pho_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/KVL_1803_phobius.results.txt", header=FALSE)
pho_1803_t <- pho_1803 %>% filter(V3 == "Y")
pho_1803_s <- pho_1803 %>% filter(V2 > 0)
pho_1803_t[ , 2:4] <- NULL
pho_1803_s[ , 2:4] <- NULL

tmhmm_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/KVL_1803_tmhmm.results", header=FALSE)
tmhmm_1803 <- separate(data = tmhmm_1803, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1803 <- tmhmm_1803 %>% filter(value > 0)
tmhmm_1803[ , 2:7] <- NULL

KVL_1803_sec <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.secretome.txt", header=FALSE)
KVL_1803_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1803 <- rbind(KVL_1803_sec, pho_1803_s)
sec_1803 <- distinct(sec_1803, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1803 <- as.data.frame(sec_1803[!(sec_1803$V1 %in% tmhmm_1803$V1),])
names(sec_1803)[names(sec_1803) == "sec_1803[!(sec_1803$V1 %in% tmhmm_1803$V1), ]"] <- "V1"
sec_1803 <- as.data.frame(sec_1803[!(sec_1803$V1 %in% pho_1803_t$V1),])
names(sec_1803)[names(sec_1803) == "sec_1803[!(sec_1803$V1 %in% pho_1803_t$V1), ]"] <- "V1"

#KVL_1806
pho_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/KVL_1806_phobius.results.txt", header=FALSE)
pho_1806_t <- pho_1806 %>% filter(V3 == "Y")
pho_1806_s <- pho_1806 %>% filter(V2 > 0)
pho_1806_t[ , 2:4] <- NULL
pho_1806_s[ , 2:4] <- NULL

tmhmm_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/KVL_1806_tmhmm.results", header=FALSE)
tmhmm_1806 <- separate(data = tmhmm_1806, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1806 <- tmhmm_1806 %>% filter(value > 0)
tmhmm_1806[ , 2:7] <- NULL

KVL_1806_sec <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.secretome.txt", header=FALSE)
KVL_1806_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1806 <- rbind(KVL_1806_sec, pho_1806_s)
sec_1806 <- distinct(sec_1806, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1806 <- as.data.frame(sec_1806[!(sec_1806$V1 %in% tmhmm_1806$V1),])
names(sec_1806)[names(sec_1806) == "sec_1806[!(sec_1806$V1 %in% tmhmm_1806$V1), ]"] <- "V1"
sec_1806 <- as.data.frame(sec_1806[!(sec_1806$V1 %in% pho_1806_t$V1),])
names(sec_1806)[names(sec_1806) == "sec_1806[!(sec_1806$V1 %in% pho_1806_t$V1), ]"] <- "V1"

#KVL_1807
pho_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/KVL_1807_phobius.results.txt", header=FALSE)
pho_1807_t <- pho_1807 %>% filter(V3 == "Y")
pho_1807_s <- pho_1807 %>% filter(V2 > 0)
pho_1807_t[ , 2:4] <- NULL
pho_1807_s[ , 2:4] <- NULL

tmhmm_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/KVL_1807_tmhmm.results", header=FALSE)
tmhmm_1807 <- separate(data = tmhmm_1807, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1807 <- tmhmm_1807 %>% filter(value > 0)
tmhmm_1807[ , 2:7] <- NULL

KVL_1807_sec <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.secretome.txt", header=FALSE)
KVL_1807_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1807 <- rbind(KVL_1807_sec, pho_1807_s)
sec_1807 <- distinct(sec_1807, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1807 <- as.data.frame(sec_1807[!(sec_1807$V1 %in% tmhmm_1807$V1),])
names(sec_1807)[names(sec_1807) == "sec_1807[!(sec_1807$V1 %in% tmhmm_1807$V1), ]"] <- "V1"
sec_1807 <- as.data.frame(sec_1807[!(sec_1807$V1 %in% pho_1807_t$V1),])
names(sec_1807)[names(sec_1807) == "sec_1807[!(sec_1807$V1 %in% pho_1807_t$V1), ]"] <- "V1"

#KVL_1808
pho_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/KVL_1808_phobius.results.txt", header=FALSE)
pho_1808_t <- pho_1808 %>% filter(V3 == "Y")
pho_1808_s <- pho_1808 %>% filter(V2 > 0)
pho_1808_t[ , 2:4] <- NULL
pho_1808_s[ , 2:4] <- NULL

tmhmm_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/KVL_1808_tmhmm.results", header=FALSE)
tmhmm_1808 <- separate(data = tmhmm_1808, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1808 <- tmhmm_1808 %>% filter(value > 0)
tmhmm_1808[ , 2:7] <- NULL

KVL_1808_sec <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.secretome.txt", header=FALSE)
KVL_1808_sec[ , 2:4] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
sec_1808 <- rbind(KVL_1808_sec, pho_1808_s)
sec_1808 <- distinct(sec_1808, V1, .keep_all = TRUE)

#remove proteins from tmhmm (transmembrane) and phobius transmembrane protiens
sec_1808 <- as.data.frame(sec_1808[!(sec_1808$V1 %in% tmhmm_1808$V1),])
names(sec_1808)[names(sec_1808) == "sec_1808[!(sec_1808$V1 %in% tmhmm_1808$V1), ]"] <- "V1"
sec_1808 <- as.data.frame(sec_1808[!(sec_1808$V1 %in% pho_1808_t$V1),])
names(sec_1808)[names(sec_1808) == "sec_1808[!(sec_1808$V1 %in% pho_1808_t$V1), ]"] <- "V1"

#Normal analysis
sec <- "sec"
sec_1801$sec_1 <- sec
sec_1802$sec_2 <- sec
sec_1803$sec_3 <- sec
sec_1806$sec_6 <- sec
sec_1807$sec_7 <- sec
sec_1808$sec_8 <- sec

names(sec_1801)[names(sec_1801) == "V1"] <- "id"
names(sec_1802)[names(sec_1802) == "V1"] <- "id"
names(sec_1803)[names(sec_1803) == "V1"] <- "id"
names(sec_1806)[names(sec_1806) == "V1"] <- "id"
names(sec_1807)[names(sec_1807) == "V1"] <- "id"
names(sec_1808)[names(sec_1808) == "V1"] <- "id"

sec_MAC <- merge(MAC_noref, sec_1801, by="id", all.x = TRUE)
sec_MAC <- merge(sec_MAC, sec_1802, by="id", all.x = TRUE)
sec_MAC <- merge(sec_MAC, sec_1803, by="id", all.x = TRUE)
sec_MAC <- merge(sec_MAC, sec_1806, by="id", all.x = TRUE)
sec_MAC <- merge(sec_MAC, sec_1807, by="id", all.x = TRUE)
sec_MAC <- merge(sec_MAC, sec_1808, by="id", all.x = TRUE)

sec_MAC$sec <- paste(sec_MAC$sec_1, "", sec_MAC$sec_2, "", sec_MAC$sec_3, "", sec_MAC$sec_6, "", sec_MAC$sec_7, "", sec_MAC$sec_8)
sec_MAC[ , 4:9] <- NULL
sec_MAC$sec<-gsub("NA","",as.character(sec_MAC$sec))
sec_MAC$sec<-gsub(" ","",as.character(sec_MAC$sec))

sec_MAC["sec"][sec_MAC["sec"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
sec_MAC$id <- NULL

sec_unique <- sec_MAC %>%
  count(Orthogroup, category, sec, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = sec[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
sec_summary <- sec_unique %>% group_by(category, first) %>% tally()

sec_total <- sec_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
sec_total$first <- total

sec_all <- rbind(sec_summary, sec_total)

sec_pivot <- sec_all %>% pivot_wider(names_from = first, values_from = n)
sec_pivot$percent <- (sec_pivot$sec/sec_pivot$total) * 100

sec_pivot$category <- factor(sec_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_sec <- ggbarstats(data = sec_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_sec
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

sec_plot <- ggplot(sec_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
sec_plot

#chi square test
sec_test <- chisq.test(table(sec_unique$category, sec_unique$first))
sec_test
pairwise_prop_test(table(sec_unique$category, sec_unique$first), p.adjust.method = "BH")

#Fisher's test
fisher.test(table(sec_unique$category, sec_unique$first))
fisher.multcomp(table(sec_unique$category, sec_unique$first))

#export sec files for effector p analysis 
sec_1801$sec_1 <- NULL
sec_1802$sec_2 <- NULL
sec_1803$sec_3 <- NULL
sec_1806$sec_6 <- NULL
sec_1807$sec_7 <- NULL
sec_1808$sec_8 <- NULL

#write.table(sec_1801, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1801.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)
#write.table(sec_1802, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1802.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)
#write.table(sec_1803, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1803.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)
#write.table(sec_1806, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1806.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)
#write.table(sec_1807, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1807.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)
#write.table(sec_1808, "/Users/mbs625/Documents/PhD/Pangenome/Analyses/funfinder/sec_1808.txt",row.names=FALSE, col.names = FALSE, sep="\t", quote = FALSE)

```


Perform the same analysis for effectors, but be sure to use effectors as predicted with the fungal method. 
```{r}
eff_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/eff_F_1801.txt", header=FALSE, comment.char="#")
eff_1801$V4 <- gsub("Y.*", "None", eff_1801$V4)
eff_1801<-eff_1801[!(eff_1801$V4=="None"),]
eff_1801[, 2:5] <- NULL
eff_1801$V1 <- gsub("FUN", "MAC1", eff_1801$V1)

eff_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/eff_F_1802.txt", header=FALSE, comment.char="#")
eff_1802$V4 <- gsub("Y.*", "None", eff_1802$V4)
eff_1802<-eff_1802[!(eff_1802$V4=="None"),]
eff_1802[, 2:5] <- NULL
eff_1802$V1 <- gsub("FUN", "MAC2", eff_1802$V1)

eff_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/eff_F_1803.txt", header=FALSE, comment.char="#")
eff_1803$V4 <- gsub("Y.*", "None", eff_1803$V4)
eff_1803<-eff_1803[!(eff_1803$V4=="None"),]
eff_1803[, 2:5] <- NULL
eff_1803$V1 <- gsub("FUN", "MAC3", eff_1803$V1)

eff_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/eff_F_1806.txt", header=FALSE, comment.char="#")
eff_1806$V4 <- gsub("Y.*", "None", eff_1806$V4)
eff_1806<-eff_1806[!(eff_1806$V4=="None"),]
eff_1806[, 2:5] <- NULL
eff_1806$V1 <- gsub("FUN", "MAC6", eff_1806$V1)

eff_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/eff_F_1807.txt", header=FALSE, comment.char="#")
eff_1807$V4 <- gsub("Y.*", "None", eff_1807$V4)
eff_1807<-eff_1807[!(eff_1807$V4=="None"),]
eff_1807[, 2:5] <- NULL
eff_1807$V1 <- gsub("FUN", "MAC7", eff_1807$V1)

eff_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/eff_F_1808.txt", header=FALSE, comment.char="#")
eff_1808$V4 <- gsub("Y.*", "None", eff_1808$V4)
eff_1808<-eff_1808[!(eff_1808$V4=="None"),]
eff_1808[, 2:5] <- NULL
eff_1808$V1 <- gsub("FUN", "MAC8", eff_1808$V1)

#change name of column for merging
names(eff_1801)[names(eff_1801) == "V1"] <- "id"
names(eff_1802)[names(eff_1802) == "V1"] <- "id"
names(eff_1803)[names(eff_1803) == "V1"] <- "id"
names(eff_1806)[names(eff_1806) == "V1"] <- "id"
names(eff_1807)[names(eff_1807) == "V1"] <- "id"
names(eff_1808)[names(eff_1808) == "V1"] <- "id"

eff <- "eff"
eff_1801$eff_1 <- eff
eff_1802$eff_2 <- eff
eff_1803$eff_3 <- eff
eff_1806$eff_6 <- eff
eff_1807$eff_7 <- eff
eff_1808$eff_8 <- eff

eff_MAC <- merge(MAC_noref, eff_1801, by="id", all.x = TRUE)
eff_MAC <- merge(eff_MAC, eff_1802, by="id", all.x = TRUE)
eff_MAC <- merge(eff_MAC, eff_1803, by="id", all.x = TRUE)
eff_MAC <- merge(eff_MAC, eff_1806, by="id", all.x = TRUE)
eff_MAC <- merge(eff_MAC, eff_1807, by="id", all.x = TRUE)
eff_MAC <- merge(eff_MAC, eff_1808, by="id", all.x = TRUE)

eff_MAC$eff <- paste(eff_MAC$eff_1, "", eff_MAC$eff_2, "", eff_MAC$eff_3, "", eff_MAC$eff_6, "", eff_MAC$eff_7, "", eff_MAC$eff_8)
eff_MAC[ , 4:9] <- NULL
eff_MAC$eff<-gsub("NA","",as.character(eff_MAC$eff))
eff_MAC$eff<-gsub(" ","",as.character(eff_MAC$eff))

eff_MAC["eff"][eff_MAC["eff"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
eff_MAC$id <- NULL

eff_unique <- eff_MAC %>%
  count(Orthogroup, category, eff, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = eff[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
eff_summary <- eff_unique %>% group_by(category, first) %>% tally()

eff_total <- eff_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
eff_total$first <- total

eff_all <- rbind(eff_summary, eff_total)

eff_pivot <- eff_all %>% pivot_wider(names_from = first, values_from = n)
eff_pivot$percent <- (eff_pivot$eff/eff_pivot$total) * 100

eff_pivot$category <- factor(eff_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_eff <- ggbarstats(data = eff_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_eff
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

eff_plot <- ggplot(eff_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
eff_plot

#chi square test
eff_test <- chisq.test(table(eff_unique$category, eff_unique$first))
eff_test
pairwise_prop_test(table(eff_unique$category, eff_unique$first), p.adjust.method = "BH")

#Fisher's test
fisher.test(table(eff_unique$category, eff_unique$first))
fisher.multcomp(table(eff_unique$category, eff_unique$first))

```

Perform the same analysis for MEROPS
```{r}
merops_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.merops.txt", header=FALSE)
merops_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.merops.txt", header=FALSE)
merops_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.merops.txt", header=FALSE)
merops_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.merops.txt", header=FALSE)
merops_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.merops.txt", header=FALSE)
merops_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.merops.txt", header=FALSE)

#change name of column for merging
names(merops_1801)[names(merops_1801) == "V1"] <- "id"
names(merops_1802)[names(merops_1802) == "V1"] <- "id"
names(merops_1803)[names(merops_1803) == "V1"] <- "id"
names(merops_1806)[names(merops_1806) == "V1"] <- "id"
names(merops_1807)[names(merops_1807) == "V1"] <- "id"
names(merops_1808)[names(merops_1808) == "V1"] <- "id"
merops_1801[ , 2:3] <- NULL
merops_1802[ , 2:3] <- NULL
merops_1803[ , 2:3] <- NULL
merops_1806[ , 2:3] <- NULL
merops_1807[ , 2:3] <- NULL
merops_1808[ , 2:3] <- NULL

merops <- "merops"
merops_1801$merops_1 <- merops
merops_1802$merops_2 <- merops
merops_1803$merops_3 <- merops
merops_1806$merops_6 <- merops
merops_1807$merops_7 <- merops
merops_1808$merops_8 <- merops

merops_MAC <- merge(MAC_noref, merops_1801, by="id", all.x = TRUE)
merops_MAC <- merge(merops_MAC, merops_1802, by="id", all.x = TRUE)
merops_MAC <- merge(merops_MAC, merops_1803, by="id", all.x = TRUE)
merops_MAC <- merge(merops_MAC, merops_1806, by="id", all.x = TRUE)
merops_MAC <- merge(merops_MAC, merops_1807, by="id", all.x = TRUE)
merops_MAC <- merge(merops_MAC, merops_1808, by="id", all.x = TRUE)

merops_MAC$merops <- paste(merops_MAC$merops_1, "", merops_MAC$merops_2, "", merops_MAC$merops_3, "", merops_MAC$merops_6, "", merops_MAC$merops_7, "", merops_MAC$merops_8)
merops_MAC[ , 4:9] <- NULL
merops_MAC$merops<-gsub("NA","",as.character(merops_MAC$merops))
merops_MAC$merops<-gsub(" ","",as.character(merops_MAC$merops))

merops_MAC["merops"][merops_MAC["merops"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
merops_MAC$id <- NULL

merops_unique <- merops_MAC %>%
  count(Orthogroup, category, merops, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = merops[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
merops_summary <- merops_unique %>% group_by(category, first) %>% tally()

merops_total <- merops_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
merops_total$first <- total

merops_all <- rbind(merops_summary, merops_total)

merops_pivot <- merops_all %>% pivot_wider(names_from = first, values_from = n)
merops_pivot$percent <- (merops_pivot$merops/merops_pivot$total) * 100

merops_pivot$category <- factor(merops_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_merops <- ggbarstats(data = merops_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_merops
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

merops_plot <- ggplot(merops_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
merops_plot

#chi square test
merops_test <- chisq.test(table(merops_unique$category, merops_unique$first))
merops_test
pairwise_prop_test(table(merops_unique$category, merops_unique$first), p.adjust.method = "BH")

```


Perform the same analysis for metabolite
```{r}
anti_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.antismash.clusters.txt", header=FALSE)
anti_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.antismash.clusters.txt", header=FALSE)
anti_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.antismash.clusters.txt", header=FALSE)
anti_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.antismash.clusters.txt", header=FALSE)
anti_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.antismash.clusters.txt", header=FALSE)
anti_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.antismash.clusters.txt", header=FALSE)

#change name of column for merging
names(anti_1801)[names(anti_1801) == "V1"] <- "id"
names(anti_1802)[names(anti_1802) == "V1"] <- "id"
names(anti_1803)[names(anti_1803) == "V1"] <- "id"
names(anti_1806)[names(anti_1806) == "V1"] <- "id"
names(anti_1807)[names(anti_1807) == "V1"] <- "id"
names(anti_1808)[names(anti_1808) == "V1"] <- "id"
anti_1801[ , 2:3] <- NULL
anti_1802[ , 2:3] <- NULL
anti_1803[ , 2:3] <- NULL
anti_1806[ , 2:3] <- NULL
anti_1807[ , 2:3] <- NULL
anti_1808[ , 2:3] <- NULL

anti <- "anti"
anti_1801$anti_1 <- anti
anti_1802$anti_2 <- anti
anti_1803$anti_3 <- anti
anti_1806$anti_6 <- anti
anti_1807$anti_7 <- anti
anti_1808$anti_8 <- anti

anti_MAC <- merge(MAC_noref, anti_1801, by="id", all.x = TRUE)
anti_MAC <- merge(anti_MAC, anti_1802, by="id", all.x = TRUE)
anti_MAC <- merge(anti_MAC, anti_1803, by="id", all.x = TRUE)
anti_MAC <- merge(anti_MAC, anti_1806, by="id", all.x = TRUE)
anti_MAC <- merge(anti_MAC, anti_1807, by="id", all.x = TRUE)
anti_MAC <- merge(anti_MAC, anti_1808, by="id", all.x = TRUE)

anti_MAC$anti <- paste(anti_MAC$anti_1, "", anti_MAC$anti_2, "", anti_MAC$anti_3, "", anti_MAC$anti_6, "", anti_MAC$anti_7, "", anti_MAC$anti_8)
anti_MAC[ , 4:9] <- NULL
anti_MAC$anti<-gsub("NA","",as.character(anti_MAC$anti))
anti_MAC$anti<-gsub(" ","",as.character(anti_MAC$anti))

anti_MAC["anti"][anti_MAC["anti"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
anti_MAC$id <- NULL

anti_unique <- anti_MAC %>%
  count(Orthogroup, category, anti, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = anti[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
anti_summary <- anti_unique %>% group_by(category, first) %>% tally()

anti_total <- anti_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
anti_total$first <- total

anti_all <- rbind(anti_summary, anti_total)

anti_pivot <- anti_all %>% pivot_wider(names_from = first, values_from = n)
anti_pivot$percent <- (anti_pivot$anti/anti_pivot$total) * 100

anti_pivot$category <- factor(anti_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_anti <- ggbarstats(data = anti_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_anti
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

anti_plot <- ggplot(anti_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
anti_plot

#chi square test
anti_test <- chisq.test(table(anti_unique$category, anti_unique$first))
anti_test
pairwise_prop_test(table(anti_unique$category, anti_unique$first), p.adjust.method = "BH")

```

Conserved protein domains
```{r}
pfam_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.pfam.txt", header=FALSE)
ipr_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.iprscan.txt", header=FALSE)
pfam_1801[ , 2:3] <- NULL
ipr_1801[ , 2:3] <- NULL
con_1801 <- rbind(pfam_1801, ipr_1801)
con_1801 <- distinct(con_1801, V1, .keep_all = TRUE)

pfam_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.pfam.txt", header=FALSE)
ipr_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.iprscan.txt", header=FALSE)
pfam_1802[ , 2:3] <- NULL
ipr_1802[ , 2:3] <- NULL
con_1802 <- rbind(pfam_1802, ipr_1802)
con_1802 <- distinct(con_1802, V1, .keep_all = TRUE)

pfam_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.pfam.txt", header=FALSE)
ipr_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.iprscan.txt", header=FALSE)
pfam_1803[ , 2:3] <- NULL
ipr_1803[ , 2:3] <- NULL
con_1803 <- rbind(pfam_1803, ipr_1803)
con_1803 <- distinct(con_1803, V1, .keep_all = TRUE)

pfam_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.pfam.txt", header=FALSE)
ipr_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.iprscan.txt", header=FALSE)
pfam_1806[ , 2:3] <- NULL
ipr_1806[ , 2:3] <- NULL
con_1806 <- rbind(pfam_1806, ipr_1806)
con_1806 <- distinct(con_1806, V1, .keep_all = TRUE)

pfam_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.pfam.txt", header=FALSE)
ipr_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.iprscan.txt", header=FALSE)
pfam_1807[ , 2:3] <- NULL
ipr_1807[ , 2:3] <- NULL
con_1807 <- rbind(pfam_1807, ipr_1807)
con_1807 <- distinct(con_1807, V1, .keep_all = TRUE)

pfam_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.pfam.txt", header=FALSE)
ipr_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.iprscan.txt", header=FALSE)
pfam_1808[ , 2:3] <- NULL
ipr_1808[ , 2:3] <- NULL
con_1808 <- rbind(pfam_1808, ipr_1808)
con_1808 <- distinct(con_1808, V1, .keep_all = TRUE)

#conserved proteins
con <- "con"
con_1801$con_1 <- con
con_1802$con_2 <- con
con_1803$con_3 <- con
con_1806$con_6 <- con
con_1807$con_7 <- con
con_1808$con_8 <- con

names(con_1801)[names(con_1801) == "V1"] <- "id"
names(con_1802)[names(con_1802) == "V1"] <- "id"
names(con_1803)[names(con_1803) == "V1"] <- "id"
names(con_1806)[names(con_1806) == "V1"] <- "id"
names(con_1807)[names(con_1807) == "V1"] <- "id"
names(con_1808)[names(con_1808) == "V1"] <- "id"

con_MAC <- merge(MAC_noref, con_1801, by="id", all.x = TRUE)
con_MAC <- merge(con_MAC, con_1802, by="id", all.x = TRUE)
con_MAC <- merge(con_MAC, con_1803, by="id", all.x = TRUE)
con_MAC <- merge(con_MAC, con_1806, by="id", all.x = TRUE)
con_MAC <- merge(con_MAC, con_1807, by="id", all.x = TRUE)
con_MAC <- merge(con_MAC, con_1808, by="id", all.x = TRUE)

con_MAC$con <- paste(con_MAC$con_1, "", con_MAC$con_2, "", con_MAC$con_3, "", con_MAC$con_6, "", con_MAC$con_7, "", con_MAC$con_8)
con_MAC[ , 4:9] <- NULL
con_MAC$con<-gsub("NA","",as.character(con_MAC$con))
con_MAC$con<-gsub(" ","",as.character(con_MAC$con))

con_MAC["con"][con_MAC["con"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
con_MAC$id <- NULL

con_unique <- con_MAC %>%
  count(Orthogroup, category, con, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = con[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
con_summary <- con_unique %>% group_by(category, first) %>% tally()

con_total <- con_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
con_total$first <- total

con_all <- rbind(con_summary, con_total)

con_pivot <- con_all %>% pivot_wider(names_from = first, values_from = n)
con_pivot$percent <- (con_pivot$con/con_pivot$total) * 100

con_pivot$category <- factor(con_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_con <- ggbarstats(data = con_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_con
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

con_plot <- ggplot(con_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
con_plot

#chi square test
con_test <- chisq.test(table(con_unique$category, con_unique$first))
con_test
pairwise_prop_test(table(con_unique$category, con_unique$first), p.adjust.method = "BH")
```

CAZYME
```{r}
caz_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.dbCAN.txt", header=FALSE)
caz_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.dbCAN.txt", header=FALSE)
caz_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.dbCAN.txt", header=FALSE)
caz_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.dbCAN.txt", header=FALSE)
caz_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.dbCAN.txt", header=FALSE)
caz_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.dbCAN.txt", header=FALSE)

#cazyme proteins
caz_1801[ , 2:3] <- NULL
caz_1802[ , 2:3] <- NULL
caz_1803[ , 2:3] <- NULL
caz_1806[ , 2:3] <- NULL
caz_1807[ , 2:3] <- NULL
caz_1808[ , 2:3] <- NULL

caz <- "caz"
caz_1801$caz_1 <- caz
caz_1802$caz_2 <- caz
caz_1803$caz_3 <- caz
caz_1806$caz_6 <- caz
caz_1807$caz_7 <- caz
caz_1808$caz_8 <- caz

names(caz_1801)[names(caz_1801) == "V1"] <- "id"
names(caz_1802)[names(caz_1802) == "V1"] <- "id"
names(caz_1803)[names(caz_1803) == "V1"] <- "id"
names(caz_1806)[names(caz_1806) == "V1"] <- "id"
names(caz_1807)[names(caz_1807) == "V1"] <- "id"
names(caz_1808)[names(caz_1808) == "V1"] <- "id"

caz_MAC <- merge(MAC_noref, caz_1801, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1802, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1803, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1806, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1807, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1808, by="id", all.x = TRUE)

caz_MAC$caz <- paste(caz_MAC$caz_1, "", caz_MAC$caz_2, "", caz_MAC$caz_3, "", caz_MAC$caz_6, "", caz_MAC$caz_7, "", caz_MAC$caz_8)
caz_MAC[ , 4:9] <- NULL
caz_MAC$caz<-gsub("NA","",as.character(caz_MAC$caz))
caz_MAC$caz<-gsub(" ","",as.character(caz_MAC$caz))

caz_MAC["caz"][caz_MAC["caz"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
caz_MAC$id <- NULL

caz_unique <- caz_MAC %>%
  count(Orthogroup, category, caz, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = caz[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
caz_summary <- caz_unique %>% group_by(category, first) %>% tally()

caz_total <- caz_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
caz_total$first <- total

caz_all <- rbind(caz_summary, caz_total)

caz_pivot <- caz_all %>% pivot_wider(names_from = first, values_from = n)
caz_pivot$percent <- (caz_pivot$caz/caz_pivot$total) * 100

caz_pivot$category <- factor(caz_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_caz <- ggbarstats(data = caz_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_caz
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

caz_plot <- ggplot(caz_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
caz_plot

#chi square test
caz_test <- chisq.test(table(caz_unique$category, caz_unique$first))
caz_test
pairwise_prop_test(table(caz_unique$category, caz_unique$first), p.adjust.method = "BH")

#Fisher's test
fisher.test(table(caz_unique$category, caz_unique$first))
fisher.multcomp(table(caz_unique$category, caz_unique$first))
```

CAZYME components
```{r}
caz_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/annotations.dbCAN.txt", header=FALSE)
caz_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/annotations.dbCAN.txt", header=FALSE)
caz_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/annotations.dbCAN.txt", header=FALSE)
caz_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/annotations.dbCAN.txt", header=FALSE)
caz_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/annotations.dbCAN.txt", header=FALSE)
caz_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/annotations.dbCAN.txt", header=FALSE)

#cazyme proteins
caz_1801[ , 2] <- NULL
caz_1802[ , 2] <- NULL
caz_1803[ , 2] <- NULL
caz_1806[ , 2] <- NULL
caz_1807[ , 2] <- NULL
caz_1808[ , 2] <- NULL

caz_1801$V3 <- substr(caz_1801$V3, 6, 7)
caz_1802$V3 <- substr(caz_1802$V3, 6, 7)
caz_1803$V3 <- substr(caz_1803$V3, 6, 7)
caz_1806$V3 <- substr(caz_1806$V3, 6, 7)
caz_1807$V3 <- substr(caz_1807$V3, 6, 7)
caz_1808$V3 <- substr(caz_1808$V3, 6, 7)

names(caz_1801)[names(caz_1801) == "V1"] <- "id"
names(caz_1802)[names(caz_1802) == "V1"] <- "id"
names(caz_1803)[names(caz_1803) == "V1"] <- "id"
names(caz_1806)[names(caz_1806) == "V1"] <- "id"
names(caz_1807)[names(caz_1807) == "V1"] <- "id"
names(caz_1808)[names(caz_1808) == "V1"] <- "id"

names(caz_1801)[names(caz_1801) == "V3"] <- "K1"
names(caz_1802)[names(caz_1802) == "V3"] <- "K2"
names(caz_1803)[names(caz_1803) == "V3"] <- "K3"
names(caz_1806)[names(caz_1806) == "V3"] <- "K6"
names(caz_1807)[names(caz_1807) == "V3"] <- "K7"
names(caz_1808)[names(caz_1808) == "V3"] <- "K8"

caz_MAC <- merge(MAC_noref, caz_1801, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1802, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1803, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1806, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1807, by="id", all.x = TRUE)
caz_MAC <- merge(caz_MAC, caz_1808, by="id", all.x = TRUE)

caz_MAC$caz <- paste(caz_MAC$K1, "", caz_MAC$K2, "", caz_MAC$K3, "", caz_MAC$K6, "", caz_MAC$K7, "", caz_MAC$K8)
caz_MAC[ , 4:9] <- NULL
caz_MAC$caz<-gsub("NA","",as.character(caz_MAC$caz))
caz_MAC$caz<-gsub(" ","",as.character(caz_MAC$caz))

caz_MAC <- caz_MAC[-which(caz_MAC$caz == ""), ]

caz_unique <- caz_MAC %>%
  count(Orthogroup, category, caz, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = caz[1], category = category[1])

caz_summary <- caz_unique %>% group_by(category, first) %>% tally()

caz_summary$category <- factor(caz_summary$category, levels = c("core", "accessory", "singleton"))

cols <- c("#B33C2C", "#C0B72D", "#47DB32", "#32DADB", "#324ADB", "#D632DB")

caz_dist <- ggplot(caz_summary, aes(fill=first, y=n, x=category)) + 
    geom_bar(position="fill", stat="identity") +
    scale_fill_manual(values = cols) +
    scale_y_reverse() +
    theme_minimal()
caz_dist
```



Transmembrane proteins
```{r}
#KVL_1801
pho_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/KVL_1801_phobius.results.txt", header=FALSE)
pho_1801_t <- pho_1801 %>% filter(V3 == "Y")
pho_1801_s <- pho_1801 %>% filter(V2 > 0)
pho_1801_t[ , 2:4] <- NULL
pho_1801_s[ , 2:4] <- NULL

tmhmm_1801 <- read.delim("/d01_KVL_data_subsets/KVL_1801/KVL_1801_tmhmm.results", header=FALSE)
tmhmm_1801 <- separate(data = tmhmm_1801, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1801 <- tmhmm_1801 %>% filter(value > 0)
tmhmm_1801[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1801 <- rbind(pho_1801_t, tmhmm_1801)
tran_1801 <- distinct(tran_1801, V1, .keep_all = TRUE)

#KVL_1802
pho_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/KVL_1802_phobius.results.txt", header=FALSE)
pho_1802_t <- pho_1802 %>% filter(V3 == "Y")
pho_1802_s <- pho_1802 %>% filter(V2 > 0)
pho_1802_t[ , 2:4] <- NULL
pho_1802_s[ , 2:4] <- NULL

tmhmm_1802 <- read.delim("/d01_KVL_data_subsets/KVL_1802/KVL_1802_tmhmm.results", header=FALSE)
tmhmm_1802 <- separate(data = tmhmm_1802, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1802 <- tmhmm_1802 %>% filter(value > 0)
tmhmm_1802[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1802 <- rbind(pho_1802_t, tmhmm_1802)
tran_1802 <- distinct(tran_1802, V1, .keep_all = TRUE)

#KVL_1803
pho_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/KVL_1803_phobius.results.txt", header=FALSE)
pho_1803_t <- pho_1803 %>% filter(V3 == "Y")
pho_1803_s <- pho_1803 %>% filter(V2 > 0)
pho_1803_t[ , 2:4] <- NULL
pho_1803_s[ , 2:4] <- NULL

tmhmm_1803 <- read.delim("/d01_KVL_data_subsets/KVL_1803/KVL_1803_tmhmm.results", header=FALSE)
tmhmm_1803 <- separate(data = tmhmm_1803, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1803 <- tmhmm_1803 %>% filter(value > 0)
tmhmm_1803[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1803 <- rbind(pho_1803_t, tmhmm_1803)
tran_1803 <- distinct(tran_1803, V1, .keep_all = TRUE)

#KVL_1806
pho_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/KVL_1806_phobius.results.txt", header=FALSE)
pho_1806_t <- pho_1806 %>% filter(V3 == "Y")
pho_1806_s <- pho_1806 %>% filter(V2 > 0)
pho_1806_t[ , 2:4] <- NULL
pho_1806_s[ , 2:4] <- NULL

tmhmm_1806 <- read.delim("/d01_KVL_data_subsets/KVL_1806/KVL_1806_tmhmm.results", header=FALSE)
tmhmm_1806 <- separate(data = tmhmm_1806, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1806 <- tmhmm_1806 %>% filter(value > 0)
tmhmm_1806[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1806 <- rbind(pho_1806_t, tmhmm_1806)
tran_1806 <- distinct(tran_1806, V1, .keep_all = TRUE)

#KVL_1807
pho_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/KVL_1807_phobius.results.txt", header=FALSE)
pho_1807_t <- pho_1807 %>% filter(V3 == "Y")
pho_1807_s <- pho_1807 %>% filter(V2 > 0)
pho_1807_t[ , 2:4] <- NULL
pho_1807_s[ , 2:4] <- NULL

tmhmm_1807 <- read.delim("/d01_KVL_data_subsets/KVL_1807/KVL_1807_tmhmm.results", header=FALSE)
tmhmm_1807 <- separate(data = tmhmm_1807, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1807 <- tmhmm_1807 %>% filter(value > 0)
tmhmm_1807[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1807 <- rbind(pho_1807_t, tmhmm_1807)
tran_1807 <- distinct(tran_1807, V1, .keep_all = TRUE)

#KVL_1808
pho_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/KVL_1808_phobius.results.txt", header=FALSE)
pho_1808_t <- pho_1808 %>% filter(V3 == "Y")
pho_1808_s <- pho_1808 %>% filter(V2 > 0)
pho_1808_t[ , 2:4] <- NULL
pho_1808_s[ , 2:4] <- NULL

tmhmm_1808 <- read.delim("/d01_KVL_data_subsets/KVL_1808/KVL_1808_tmhmm.results", header=FALSE)
tmhmm_1808 <- separate(data = tmhmm_1808, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1808 <- tmhmm_1808 %>% filter(value > 0)
tmhmm_1808[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1808 <- rbind(pho_1808_t, tmhmm_1808)
tran_1808 <- distinct(tran_1808, V1, .keep_all = TRUE)

#Analysis
tran <- "tran"
tran_1801$tran_1 <- tran
tran_1802$tran_2 <- tran
tran_1803$tran_3 <- tran
tran_1806$tran_6 <- tran
tran_1807$tran_7 <- tran
tran_1808$tran_8 <- tran

names(tran_1801)[names(tran_1801) == "V1"] <- "id"
names(tran_1802)[names(tran_1802) == "V1"] <- "id"
names(tran_1803)[names(tran_1803) == "V1"] <- "id"
names(tran_1806)[names(tran_1806) == "V1"] <- "id"
names(tran_1807)[names(tran_1807) == "V1"] <- "id"
names(tran_1808)[names(tran_1808) == "V1"] <- "id"

tran_MAC <- merge(MAC_noref, tran_1801, by="id", all.x = TRUE)
tran_MAC <- merge(tran_MAC, tran_1802, by="id", all.x = TRUE)
tran_MAC <- merge(tran_MAC, tran_1803, by="id", all.x = TRUE)
tran_MAC <- merge(tran_MAC, tran_1806, by="id", all.x = TRUE)
tran_MAC <- merge(tran_MAC, tran_1807, by="id", all.x = TRUE)
tran_MAC <- merge(tran_MAC, tran_1808, by="id", all.x = TRUE)

tran_MAC$tran <- paste(tran_MAC$tran_1, "", tran_MAC$tran_2, "", tran_MAC$tran_3, "", tran_MAC$tran_6, "", tran_MAC$tran_7, "", tran_MAC$tran_8)
tran_MAC[ , 4:9] <- NULL
tran_MAC$tran<-gsub("NA","",as.character(tran_MAC$tran))
tran_MAC$tran<-gsub(" ","",as.character(tran_MAC$tran))

tran_MAC["tran"][tran_MAC["tran"] == ''] <- "None"

#Remove protein id, and remove duplicate rows
#Take the secreted category of each orthogroup depending on what occurs most often
tran_MAC$id <- NULL

tran_unique <- tran_MAC %>%
  count(Orthogroup, category, tran, sort = TRUE) %>%
  group_by(Orthogroup) %>%
  summarise(first = tran[1], category = category[1])

#the number of singletons has decreased, because we removed the reference from the analysis- everything else is the same
tran_summary <- tran_unique %>% group_by(category, first) %>% tally()

tran_total <- tran_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
tran_total$first <- total

tran_all <- rbind(tran_summary, tran_total)

tran_pivot <- tran_all %>% pivot_wider(names_from = first, values_from = n)
tran_pivot$percent <- (tran_pivot$tran/tran_pivot$total) * 100

tran_pivot$category <- factor(tran_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstat plot
gg_bar_tran <- ggbarstats(data = tran_unique, x = first, y = category) + labs(caption = NULL) 
gg_bar_tran
#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

tran_plot <- ggplot(tran_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
tran_plot

#chi square test
tran_test <- chisq.test(table(tran_unique$category, tran_unique$first))
tran_test
pairwise_prop_test(table(tran_unique$category, tran_unique$first), p.adjust.method = "BH")

#Fisher's test
fisher.test(table(tran_unique$category, tran_unique$first))
fisher.multcomp(table(tran_unique$category, tran_unique$first))

```

Find unclassified proteins

```{r}

all_prot <- rbind(anti_unique, tran_unique, sec_unique, eff_unique, con_unique, merops_unique, caz_unique)
all_prot %>% group_by(first) %>% tally()
label <- all_prot %>% filter(first != "None")
label[, 2:3] <- NULL
label <- distinct(label, Orthogroup, .keep_all = TRUE)
value <- "og_ann"
label$og_ann <- value

MAC_noref <- all_MAC[!grepl("EF", all_MAC$id),]
MAC_og_noref <- distinct(MAC_noref, Orthogroup, .keep_all = TRUE)
MAC_og_noref[, 2:3] <- NULL

no_ann_MAC <- merge(label, MAC_og_noref, by="Orthogroup", all.y = TRUE)
no_ann_MAC$og_ann <- no_ann_MAC$og_ann %>% replace_na("none")

empty_MAC <- merge(MAC_noref, no_ann_MAC, by="Orthogroup")
empty_MAC$id <- NULL
empty_MAC <- empty_MAC[!duplicated(empty_MAC), ]

#create pivot table for graph
empty_summary <- empty_MAC %>% group_by(category, og_ann) %>% tally()

empty_total <- empty_summary %>% group_by(category) %>% 
  summarise(n = sum(n))
total <- "total"
empty_total$first <- total
names(empty_summary)[names(empty_summary) == "og_ann"] <- "first"

empty_all <- rbind(empty_summary, empty_total)

empty_pivot <- empty_all %>% pivot_wider(names_from = first, values_from = n)
empty_pivot$percent <- (empty_pivot$none/empty_pivot$total) * 100

empty_pivot$category <- factor(empty_pivot$category, levels = c("core", "accessory", "singleton"))

#ggstatsplot
gg_bar_empty <- ggbarstats(data = empty_MAC, x = og_ann, y = category) + labs(caption = NULL) 
gg_bar_empty

#make plot 
cols_2 <- c("#ff9d9d", "#ff0000", "#8b0000")

empty_plot <- ggplot(empty_pivot, aes(x=category, y=percent, fill =category)) +
  geom_bar(stat = "identity", alpha = 0.8) +
    scale_fill_manual(values = cols_2) +
    theme(legend.position="none") +
    theme_minimal()
empty_plot

#chi square test
empty_test <- chisq.test(table(empty_MAC$category, empty_MAC$og_ann))
empty_test
pairwise_prop_test(table(empty_MAC$category, empty_MAC$og_ann), p.adjust.method = "BH")

#Fisher's test
fisher.test(table(empty_MAC$category, empty_MAC$og_ann))
fisher.multcomp(table(empty_MAC$category, empty_MAC$og_ann))
```
