---
title: "KVL_1801_acc_core"
output: html_document
date: "2023-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(stringr)
library(tidyr)
library(viridis)
library(ggstatsplot) 
library(ggstatsplot) 
library(rstatix)
library(RVAideMemoire)
library(GOstats)
library(AnnotationForge)
library(GSEABase)
library(plyr)
```

Create Metarhizium acridum datatable for orthogroups

```{r}
unassigned <- read.delim("Figure_2/Orthogroups_UnassignedGenes.tsv")
orthogroups <- read.delim("Figure_2/Orthogroups.tsv")

all_ortho <- rbind(orthogroups, unassigned)

mac <- all_ortho[c(1,2,18:23)]
mac[mac == ''] <- NA
mac_rm <- mac[rowSums(is.na(mac)) != 7, ]  

mac_rm$M.acridum_GCA_000187405.1 <- mac_rm$GCA_000187405.1
mac_rm$GCA_000187405.1 <- NULL

mac_binary <- mac_rm[ , 2:8]

mac_binary[mac_binary != "*"] = 1
mac_binary <- mac_binary %>% replace(is.na(.), 0)

mac_binary <- mutate_all(mac_binary, function(x) as.numeric(as.character(x)))
mac_binary$total <- rowSums(mac_binary)

p <- mac_binary %>% dplyr::count(total, sort = TRUE)
```

Determine number of singletons in each isolate
```{r}
singletons <- mac_binary %>% filter(total == 1) 

mac_singletons <- as.data.frame(colSums(singletons))
mac_singletons$isolate <- rownames(mac_singletons)
mac_singletons <- mac_singletons[-8,]
mac_singletons$count <- mac_singletons$`colSums(singletons)`

mac_singlebar <- ggplot(mac_singletons) +
  geom_bar(stat = "identity", fill="#8b0000", aes(x=isolate, y=count)) +
  theme_minimal()
```

Make tables for core, accessory, and singleton orthogroups 
```{r}
ortho_list <- mac_rm$Orthogroup
mac_binary$Orthogroup <- ortho_list

singletons <- mac_binary %>% filter(total == 1) 
core <- mac_binary %>% filter(total == 7) 
accessory <- mac_binary %>% filter(total < 7, total > 1)

single_ortho <- singletons$Orthogroup
core_ortho <- core$Orthogroup
acc_ortho <- accessory$Orthogroup

mac_rm$KVL_1801<-gsub("FUN","MAC1",as.character(mac_rm$KVL_1801))
mac_rm$KVL_1802<-gsub("FUN","MAC2",as.character(mac_rm$KVL_1802))
mac_rm$KVL_1803<-gsub("FUN","MAC3",as.character(mac_rm$KVL_1803))
mac_rm$KVL_1806<-gsub("FUN","MAC6",as.character(mac_rm$KVL_1806))
mac_rm$KVL_1807<-gsub("FUN","MAC7",as.character(mac_rm$KVL_1807))
mac_rm$KVL_1808<-gsub("FUN","MAC8",as.character(mac_rm$KVL_1808))

mac_rm$proteins <- apply(
  mac_rm[, c("KVL_1801","KVL_1802","KVL_1803",
             "KVL_1806","KVL_1807","KVL_1808",
             "M.acridum_GCA_000187405.1")],
  1,
  function(x) paste(na.omit(x), collapse = ",")
)

mac_proteins <- mac_rm %>%
  tidyr::separate_rows(proteins, sep = ",")

mac_long <- mac_proteins %>%
  dplyr::rename(id = proteins) %>%
  mutate(id = trimws(id)) %>%
  filter(id != "", !is.na(id))

single_df <- mac_long[mac_long$Orthogroup %in% single_ortho,]
acc_df <- mac_long[mac_long$Orthogroup %in% acc_ortho,]
core_df <- mac_long[mac_long$Orthogroup %in% core_ortho,]

#Label
MAC_length <- read.delim("Figure_3/d02_MAC_length.txt", header=FALSE)
MAC_length$id <- MAC_length$V1 
MAC_length$V1 <- NULL

name1 <- "singletons"
name2 <- "accessory"
name3 <- "core"

single_df$category <- name1
acc_df$category <- name2
core_df$category <- name3

all_MAC <- rbind(single_df, acc_df, core_df)

MAC_merge <- merge(MAC_length,all_MAC,by="id", all.x = TRUE)

MAC_core <- MAC_merge %>% filter(category == "core")
MAC_acc <- MAC_merge %>% filter(category == "accessory")
MAC_sin <- MAC_merge %>% filter(category == "singletons")

#remove reference genome from merged datatable
all_MAC <- rbind(single_df, acc_df, core_df)
MAC_noref <- all_MAC[!grepl("FUN", all_MAC$id),]
```

Identify proteins in KVL_1801 that are on accessory scaffolds
```{r}
MAC_1801 <- read.delim("/d01d_Metarhizium_acridum_KVL_1801_H324.gff3", header=FALSE, comment.char="#")
M1801 <- "MAC_1801"
MAC_1801$genome <- M1801
MAC_1801$V9 <- gsub("FUN", "MAC1", MAC_1801$V9)
MAC_1801$V3 <- as.factor(MAC_1801$V3)
MAC_1801 <- filter(MAC_1801, V3 == "gene")

#extract relevant columns from merged gff3 file
MAC_1801 <- as.data.frame(cbind(MAC_1801$V1, MAC_1801$V4, MAC_1801$V5, MAC_1801$V9, MAC_1801$genome))
MAC_1801$V4 <- gsub("ID=", "", MAC_1801$V4)
MAC_1801$V4 <- gsub(";.*","", MAC_1801$V4)

#Add column detailing accessory or core chromosomes
MAC_1801$compartment <- NA
MAC_1801$compartment <- replace_na("core_chr")
MAC_1801$compartment[MAC_1801$V1=="chr_8"] <- "acc_chr"
MAC_1801$compartment[MAC_1801$V1=="chr_9"] <- "acc_chr"
MAC_1801$compartment[MAC_1801$V1=="chr_11"] <- "acc_chr"
MAC_1801$compartment[MAC_1801$V1=="chr_12"] <- "acc_chr"
```

Create a table merging KVL 1801 and MAC_noref
```{r}
MAC_1801_comp <- MAC_noref
MAC_1801_comp$genome <- MAC_1801_comp$id
MAC_1801_comp$genome <- gsub("_.*", "", MAC_1801_comp$genome)

MAC_1801_comp <- MAC_1801_comp %>%
  filter(genome == "MAC1")
MAC_1801_comp$id <- gsub("-T1", "", MAC_1801_comp$id)

MAC_1801_total <- MAC_1801 %>% left_join(MAC_1801_comp, 
                                          by=c("V4" = "id"))
#there are some NAs because these represent tRNAs which are not included in the fasta file but are in the gff3 file
names(MAC_1801_total)[names(MAC_1801_total) == "V4"] <- "id"

MAC_1801_total$category <- factor(MAC_1801_total$category, levels = c("core", "accessory", "singletons"))
```


Now we'll make bar graphs for the different genome compartments

Core, singleton, accessory
```{r}
#make summary table
summary_comp_1801 <- MAC_1801_total %>% group_by(compartment, category) %>% dplyr::tally()
comp_total_1801 <- summary_comp_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
comp_total_1801$category <- total

comp_all_1801 <- rbind(summary_comp_1801, comp_total_1801)

comp_pivot <- comp_all_1801 %>% pivot_wider(names_from = category, values_from = n)
comp_pivot$acc_percent <- (comp_pivot$accessory/comp_pivot$total) * 100
comp_pivot$sin_percent <- (comp_pivot$singletons/comp_pivot$total) * 100
comp_pivot$core_percent <- (comp_pivot$core/comp_pivot$total) * 100

#ggstat plot
gg_bar_comp <- ggbarstats(data = MAC_1801_total, x = category, y = compartment) + labs(caption = NULL) 
gg_bar_comp

comp_all <- subset(comp_all_1801, category!= "total")
comp_all$category <- factor(comp_all$category, levels = c("singletons", "accessory", "core"))
comp_all = ddply(comp_all, .(compartment), transform, percent = n/sum(n) * 100)

cols_2 <- c("#8b0000","#ff0000","#ff9d9d")
comp_plot <- ggplot(comp_all, aes(x = compartment, y = n, fill = category)) +
  geom_bar(position="fill", stat="identity", alpha = 0.8) +
  scale_fill_manual(values = cols_2) +
  labs(x = "ARSEF 3391", y = "Proportion of genome (%)") +
    theme_minimal()

comp_plot

```


Secretome
```{r}
#import secretome file
sec_1801 <- read.delim("d01e_annotations.secretome.txt", header=FALSE)
sec_1801[, 2:3] <- NULL

#change name of column for merging
names(sec_1801)[names(sec_1801) == "V1"] <- "id"
sec_1801$id <- gsub("-T1", "", sec_1801$id)

#add column
sec_1801$sec <- "sec"

#merge tables
sec_MAC <- merge(MAC_1801_total, sec_1801, by="id", all.x = TRUE)
sec_MAC$sec <- sec_MAC$sec %>% replace_na("None")

#make summary table
summary_sec_1801 <- sec_MAC %>% group_by(compartment, sec) %>% tally()
sec_total_1801 <- summary_sec_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
sec_total_1801$sec <- total

sec_all_1801 <- rbind(summary_sec_1801, sec_total_1801)

sec_pivot <- sec_all_1801 %>% pivot_wider(names_from = sec, values_from = n)
sec_pivot[is.na(sec_pivot)] = 0
sec_pivot$percent <- (sec_pivot$sec/sec_pivot$total) * 100

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

sec_plot <- ggplot(sec_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Secretome proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
sec_plot

```

Effectors 
```{r}
#import effector dataset
eff_1801 <- read.delim("d01f_eff_F_1801.txt", header=FALSE, comment.char="#")
eff_1801$V4 <- gsub("Y.*", "None", eff_1801$V4)
eff_1801<-eff_1801[!(eff_1801$V4=="None"),]
eff_1801[, 2:5] <- NULL
eff_1801$V1 <- gsub("FUN", "MAC1", eff_1801$V1)
eff_1801$V1 <- gsub("-T1", "", eff_1801$V1)
names(eff_1801)[names(eff_1801) == "V1"] <- "id"

#add column
eff_1801$eff <- "eff"

#merge label column
eff_MAC <- merge(MAC_1801_total, eff_1801, by="id", all.x = TRUE)
eff_MAC$eff <- eff_MAC$eff %>% replace_na("None")

#make summary table
summary_eff_1801 <- eff_MAC %>% group_by(compartment, eff) %>% tally()
eff_total_1801 <- summary_eff_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
eff_total_1801$eff <- total

eff_all_1801 <- rbind(summary_eff_1801, eff_total_1801)

eff_pivot <- eff_all_1801 %>% pivot_wider(names_from = eff, values_from = n)
eff_pivot[is.na(eff_pivot)] = 0
eff_pivot$percent <- (eff_pivot$eff/eff_pivot$total) * 100

#ggstat plot
gg_bar_eff <- ggbarstats(data = eff_MAC, x = eff, y = compartment) + labs(caption = NULL) 
gg_bar_eff

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

eff_plot <- ggplot(eff_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Effector proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
eff_plot
```

MEROPS
```{r}
#import dataset
merops_1801 <- read.delim("d01g_annotations.merops.txt", header=FALSE)
names(merops_1801)[names(merops_1801) == "V1"] <- "id"
merops_1801[ , 2:3] <- NULL

merops_1801$merops <- "merops"

merops_1801$id <- gsub("-T1", "", merops_1801$id)

#merge label column
merops_MAC <- merge(MAC_1801_total, merops_1801, by="id", all.x = TRUE)
merops_MAC$merops <- merops_MAC$merops %>% replace_na("None")

#make summary table
summary_merops_1801 <- merops_MAC %>% group_by(compartment, merops) %>% tally()
merops_total_1801 <- summary_merops_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
merops_total_1801$merops <- total

merops_all_1801 <- rbind(summary_merops_1801, merops_total_1801)

merops_pivot <- merops_all_1801 %>% pivot_wider(names_from = merops, values_from = n)
merops_pivot[is.na(merops_pivot)] = 0
merops_pivot$percent <- (merops_pivot$merops/merops_pivot$total) * 100

#ggstat plot
gg_bar_merops <- ggbarstats(data = merops_MAC, x = merops, y = compartment) + labs(caption = NULL) 
gg_bar_merops

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

merops_plot <- ggplot(merops_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Merops proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
merops_plot
```
Secondary metabolites
```{r}
anti_1801 <- read.delim("d01h_annotations.antismash.clusters.txt", header=FALSE)
names(anti_1801)[names(anti_1801) == "V1"] <- "id"
anti_1801[ , 2:3] <- NULL

anti_1801$anti <- "anti"

anti_1801$id <- gsub("-T1", "", anti_1801$id)

#merge label column
anti_MAC <- merge(MAC_1801_total, anti_1801, by="id", all.x = TRUE)
anti_MAC$anti <- anti_MAC$anti %>% replace_na("None")

#make summary table
summary_anti_1801 <- anti_MAC %>% group_by(compartment, anti) %>% tally()
anti_total_1801 <- summary_anti_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
anti_total_1801$anti <- total

anti_all_1801 <- rbind(summary_anti_1801, anti_total_1801)

anti_pivot <- anti_all_1801 %>% pivot_wider(names_from = anti, values_from = n)
anti_pivot[is.na(anti_pivot)] = 0
anti_pivot$percent <- (anti_pivot$anti/anti_pivot$total) * 100

#ggstat plot
gg_bar_anti <- ggbarstats(data = anti_MAC, x = anti, y = compartment) + labs(caption = NULL) 
gg_bar_anti

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

anti_plot <- ggplot(anti_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Secondary metabolite proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
anti_plot

```
Conserved protein domains

```{r}
pfam_1801 <- read.delim("d01i_annotations.pfam.txt", header=FALSE)
ipr_1801 <- read.delim("d01j_annotations.iprscan.txt", header=FALSE)
pfam_1801[ , 2:3] <- NULL
ipr_1801[ , 2:3] <- NULL
con_1801 <- rbind(pfam_1801, ipr_1801)
con_1801 <- distinct(con_1801, V1, .keep_all = TRUE)

con_1801$con <- "con"

names(con_1801)[names(con_1801) == "V1"] <- "id"
con_1801$id <- gsub("-T1", "", con_1801$id)

#merge label column
con_MAC <- merge(MAC_1801_total, con_1801, by="id", all.x = TRUE)
con_MAC$con <- con_MAC$con %>% replace_na("None")

#make summary table
summary_con_1801 <- con_MAC %>% group_by(compartment, con) %>% tally()
con_total_1801 <- summary_con_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
con_total_1801$con <- total

con_all_1801 <- rbind(summary_con_1801, con_total_1801)

con_pivot <- con_all_1801 %>% pivot_wider(names_from = con, values_from = n)
con_pivot[is.na(con_pivot)] = 0
con_pivot$percent <- (con_pivot$con/con_pivot$total) * 100

#ggstat plot
gg_bar_con <- ggbarstats(data = con_MAC, x = con, y = compartment) + labs(caption = NULL) 
gg_bar_con

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

con_plot <- ggplot(con_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Conserved protein domains (%)") 
    #geom_label(aes(label=percent), fill = "white")
con_plot
```
CAZYME

```{r}
caz_1801 <- read.delim("d01k_annotations.dbCAN.txt", header=FALSE)
caz_1801[ , 2:3] <- NULL
names(caz_1801)[names(caz_1801) == "V1"] <- "id"
caz_1801$caz <- "caz"

caz_1801$id <- gsub("-T1", "", caz_1801$id)

#merge label column
caz_MAC <- merge(MAC_1801_total, caz_1801, by="id", all.x = TRUE)
caz_MAC$caz <- caz_MAC$caz %>% replace_na("None")

#make summary table
summary_caz_1801 <- caz_MAC %>% group_by(compartment, caz) %>% tally()
caz_total_1801 <- summary_caz_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
caz_total_1801$caz <- total

caz_all_1801 <- rbind(summary_caz_1801, caz_total_1801)

caz_pivot <- caz_all_1801 %>% pivot_wider(names_from = caz, values_from = n)
caz_pivot[is.na(caz_pivot)] = 0
caz_pivot$percent <- (caz_pivot$caz/caz_pivot$total) * 100

#ggstat plot
gg_bar_caz <- ggbarstats(data = caz_MAC, x = caz, y = compartment) + labs(caption = NULL) 
gg_bar_caz

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

caz_plot <- ggplot(caz_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "CAZyme proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
caz_plot
```
Transmembrane proteins
```{r}
#KVL_1801
pho_1801 <- read.delim("d01l_KVL_1801_phobius.results.txt", header=FALSE)
pho_1801_t <- pho_1801 %>% filter(V3 == "Y")
pho_1801_s <- pho_1801 %>% filter(V2 > 0)
pho_1801_t[ , 2:4] <- NULL
pho_1801_s[ , 2:4] <- NULL

tmhmm_1801 <- read.delim("d01m_KVL_1801_tmhmm.results", header=FALSE)
tmhmm_1801 <- separate(data = tmhmm_1801, col = V5, into = c("pred", "value"), sep = "=")
tmhmm_1801 <- tmhmm_1801 %>% filter(value > 0)
tmhmm_1801[ , 2:7] <- NULL

#combine results from funannotate secretome and phobius secreted proteins
tran_1801 <- rbind(pho_1801_t, tmhmm_1801)
tran_1801 <- distinct(tran_1801, V1, .keep_all = TRUE)

tran_1801$tran <- "tran"
names(tran_1801)[names(tran_1801) == "V1"] <- "id"
tran_1801$id <- gsub("-T1", "", tran_1801$id)

#merge label column
tran_MAC <- merge(MAC_1801_total, tran_1801, by="id", all.x = TRUE)
tran_MAC$tran <- tran_MAC$tran %>% replace_na("None")

#make summary table
summary_tran_1801 <- tran_MAC %>% group_by(compartment, tran) %>% tally()
tran_total_1801 <- summary_tran_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
tran_total_1801$tran <- total

tran_all_1801 <- rbind(summary_tran_1801, tran_total_1801)

tran_pivot <- tran_all_1801 %>% pivot_wider(names_from = tran, values_from = n)
tran_pivot[is.na(tran_pivot)] = 0
tran_pivot$percent <- (tran_pivot$tran/tran_pivot$total) * 100

#ggstat plot
gg_bar_tran <- ggbarstats(data = tran_MAC, x = tran, y = compartment) + labs(caption = NULL) 
gg_bar_tran

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

tran_plot <- ggplot(tran_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Transmembrane proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
tran_plot
```
Find unclassified proteins
```{r}
names(sec_1801)[names(sec_1801) == "sec"] <- "type"
names(eff_1801)[names(eff_1801) == "eff"] <- "type"
names(merops_1801)[names(merops_1801) == "merops"] <- "type"
names(anti_1801)[names(anti_1801) == "anti"] <- "type"
names(con_1801)[names(con_1801) == "con"] <- "type"
names(caz_1801)[names(caz_1801) == "caz"] <- "type"
names(tran_1801)[names(tran_1801) == "tran"] <- "type"

all_prot <- rbind(sec_1801, eff_1801, merops_1801, anti_1801, con_1801, caz_1801, tran_1801)
all_prot$type <- NULL
all_prot <- all_prot %>% distinct()
all_prot$type <- "id"

unclass_MAC <- merge(MAC_1801_total, all_prot, by="id", all.x = TRUE)
unclass_MAC$type <- unclass_MAC$type %>% replace_na("None")

#make summary table
summary_unclass_1801 <- unclass_MAC %>% group_by(compartment, type) %>% tally()
unclass_total_1801 <- summary_unclass_1801 %>% group_by(compartment) %>% 
  dplyr::summarise(n = sum(n))
total <- "total"
unclass_total_1801$type <- total

unclass_all_1801 <- rbind(summary_unclass_1801, unclass_total_1801)

unclass_pivot <- unclass_all_1801 %>% pivot_wider(names_from = type, values_from = n)
unclass_pivot[is.na(unclass_pivot)] = 0
unclass_pivot$percent <- (unclass_pivot$None/unclass_pivot$total) * 100

#ggstat plot
gg_bar_unclass <- ggbarstats(data = unclass_MAC, x = type, y = compartment) + labs(caption = NULL) 
gg_bar_unclass

#make plot 
cols_1 <- c("#ACE1AF", "#00A86B")

unclass_plot <- ggplot(unclass_pivot, aes(x=compartment, y=percent, fill = compartment)) +
  geom_bar(stat = "identity", alpha = 0.8, show.legend = FALSE) +
    scale_fill_manual(values = cols_1) +
    theme_minimal() +
    labs (x = "ARSEF 3391", y = "Unclassified proteins (%)") 
    #geom_label(aes(label=percent), fill = "white")
unclass_plot

```

Data subset 
```{r}
MAC_1801_sub <- as.data.frame(cbind(MAC_1801_total$id, MAC_1801_total$compartment))

MAC_1801_core <- filter(MAC_1801_sub, V2 == "core_chr")
MAC_1801_acc <- filter(MAC_1801_sub, V2 == "acc_chr")

MAC_1801_core$V2 <- NULL
MAC_1801_acc$V2 <- NULL

```
